An Image-based method for phase estimation, gating and temporal super-resolution of \\cardiac ultrasound

### 2017-02-22 paper155.tex
Updated paper

	Next, considering the narrow-band nature of the respiration and heart-beat signals (see  Figure~\ref{fig:phase_estimation}(e)), we use the Hilbert transform~\cite{Lu2013} to estimate the instantaneous phase of each frame. Specifically, we compute the instantaneous intra-period phase $\phi(t) \in \left [  -\pi, \pi\right )$ of the periodic time series $x(t)$ using its Hilbert transform $H_x(t)$ as follows: $\phi(t) = arctan \left( \frac{H_x(t)}{x(t)}\right)$ and map $\phi(t)$ from the range $\left [  -\pi, \pi\right )$ to $\left [  0, 1\right )$. Let $\hat{\phi}_{heart}(t)$ and $\hat{\phi}_{resp}(t)$ denote the instantaneous cardiac and respiratory phases computed from the trend/respiration $\hat{\tau}_{resp}(t)$ and residual/heart-beat $\hat{r}_{heart}(t)$ signals, respectively. Figure~\ref{fig:phase_estimation}(f) shows the instantaneous cardiac and respiratory phases computed from the heart-beat and respiration signals in Figure~\ref{fig:phase_estimation}(d). 
%
\vspace{-0.5cm}
\subsection{Gating out respiratory frames}
\label{sec:method:gating}
%
%
\begin{IonFigT}
\centering
%
\includegraphics[width=5.0in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/respiratory_phase_gating.png}
\ionbox{5.0in}\\
\includegraphics[width=5.0in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/robust_lowess_gating.png}
\ionbox{5.0in}\\
%
\caption{Illustration of our two-step method for gating out respiratory frames: (a) Frames $F_{cutoff}$ discarded (blue circles) in the first step overlaid with the trend/respiration, residual/heart-beat, and instantaneous respiratory phase signals (b) residual/heart-beat signal $\hat{r}_{heart}(t)$ vs cardiac phase $\hat{\phi}_{heart}(t)$ overlaid with frames $F_{cutoff}$ discarded in step-1 (blue circle), LOWESS fit $L(\phi)$ (black solid), upper and lower bounds or 95\% confidence interval $(L(\phi) \pm 2.0 * \hat{\sigma}_L)$ of valid non-respiratory frames (black dotted), and frames $F_{resp}$ (red circles) gated at the end of step-2.}
\label{fig:respiratory_gating}
\end{IonFigT}
%
Once the cardiac and respiratory phases of each frame have been estimated, it can be used to filter out or guide the extraction of quantitative measurements from a desired part/point of the periodic cycle, a process commonly referred to as gating. In this section, we present a robust two-step method that uses these phase estimates to gate out video frames with significant respiratory motion.

>>>>

	Next, considering the narrow-band nature of the respiration and heart-beat signals (see  Figure~\ref{fig:phase_estimation}(e)), we use the Hilbert transform~\cite{Lu2013} to estimate the instantaneous phase of each frame. Specifically, we compute the instantaneous intra-period phase $\phi(t) \in \left [  -\pi, \pi\right )$ of a periodic time series $x(t)$ using its Hilbert transform $H_x(t)$ as follows: $\phi(t) = arctan \left( \frac{H_x(t)}{x(t)}\right)$ and map $\phi(t)$ from the range $\left [  -\pi, \pi\right )$ to $\left [  0, 1\right )$. Let $\hat{\phi}_{heart}(t)$ and $\hat{\phi}_{resp}(t)$ denote the instantaneous cardiac and respiratory phases computed from the trend/respiration $\hat{\tau}_{resp}(t)$ and residual/heart-beat $\hat{r}_{heart}(t)$ signals, respectively. Figure~\ref{fig:phase_estimation}(f) shows the instantaneous cardiac and respiratory phases computed from the heart-beat and respiration signals in Figure~\ref{fig:phase_estimation}(d). 
%
\vspace{-0.5cm}
\subsection{Gating out respiratory frames}
\label{sec:method:gating}
%
%
\begin{IonFigT}
\centering
%
\includegraphics[width=5.0in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/respiratory_phase_gating.png}
\ionbox{5.0in}\\
\includegraphics[width=5.0in]{figures/decoded/2015-07-27-10-36-06_2015-07-15-16-56-16_1.raw.bmode/robust_lowess_gating.png}
\ionbox{5.0in}\\
%
\caption{Illustration of our two-step method for gating out respiratory frames: (a) Frames $F_{cutoff}$ discarded (blue circles) in the first step overlaid with the trend/respiration, residual/heart-beat, and instantaneous respiratory phase signals (b) residual/heart-beat signal $\hat{r}_{heart}(t)$ vs cardiac phase $\hat{\phi}_{heart}(t)$ overlaid with frames $F_{cutoff}$ discarded in step-1 (blue circle), LOWESS fit $L(\phi)$ (black solid), upper and lower bounds or 95\% confidence interval $(L(\phi) \pm 2.0 * \hat{\sigma}_L)$ of valid non-respiratory frames (black dotted), and frames $F_{resp}$ (red circles) gated at the end of step-2.}
\label{fig:respiratory_gating}
\end{IonFigT}
%
Once the cardiac and respiratory phases of each frame have been estimated, it can be used to filter out or guide the extraction of quantitative measurements from a desired part/point of the periodic cycle, a process commonly referred to as gating. In this section, we present a robust two-step method that uses these phase estimates to gate out video frames with significant respiratory motion.
